Reconstructing the Lensing Mass in the Universe \\ from Photometric Catalogue Data

### 2012-12-04 doc/acknowledgments.tex

TEC acknowledges support from STFC in the form of a research studentship.
%
PJM was given support by the Kavli Foundation and the Royal 
Society, in the form of research fellowships.
%
MWA \ldots
%
SH \ldots
%
SHS \ldots
%
TT acknowledges support from the NSF through CAREER award NSF-0642621,
and from the Packard Foundation through a Packard Research Fellowship.
% 
LVEK acknowledges the support by an NWO-VIDI programme subsidy
(programme number 639.042.505).
%
This research is supported in part by the National Science Foundation under
Grant No. PHY99-07949.

>>>>

TEC acknowledges support from STFC in the form of a research studentship.
%
PJM was given support by the Kavli Foundation and the Royal 
Society, in the form of research fellowships.
%
% MWA \ldots
%
SH and RDB, and CDF, acknowledge support by the National Science Foundation
(NSF), grant numbers AST-0807458 and  AST-0909119, respectively.
%
SHS, ZG  and TT gratefully acknowledge support from the Packard Foundation in
the form of a Packard Research Fellowship to TT and from the 
NSF grant AST-0642621.
% 
LVEK acknowledges the support by an NWO-VIDI programme subsidy
(programme number 639.042.505).
%
% This research is supported in part by the National Science Foundation under
% Grant No. PHY99-07949.
%
The Millennium Simulation databases used in this paper and the web application
providing online access to them were constructed as part of the activities of
the German Astrophysical Virtual Observatory.
